### 2023-07-05 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small changes to stenosis section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). We considered a semipermeable vesicle suspended in these
same geometries~\cite{qua-gan-you2021}. All the multicomponent examples
have floppy-to-stiff ratio $\beta = 10^{-1}$. For the single-component
case, we consider two bending stiffnesses: $b(u) = 1$ and $b(u) = 0.55$
which is the average bending stiffness of a multicomponent vesicle whose
stiff and floppy regions have the same area. Throughout this section we
plot the position of the vesicle in terms of the $x$-coordinate of its
center of mass. For the stenosed geometry in
Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and
ends at $x=15$. For the contracting geometry in
Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
and reaches its narrowest point at $x=15$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Stenosis}A multicomponent vesicle in a closely-fit channel (Stenosis)}

@@

We consider a vesicle with reduced area $\alpha = 0.6$ passing through a
closely-fitting channel (stenosis), with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a multicomponent
vesicle with an initially random distribution of lipids. In all plots,
the color is the dimensionless bending modulus of the multicomponent
vesicle that remains bounded in $[0.1,1]$ by using the new bending
modulus~\eqref{eqn:tanhBending}. A single Lagrangian point is included
to visualize tank-treading behavior. There are slight differences
between the three cases, with the most noticeable being that the
multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. The main difference between the two reduced
areas is that the vesicles with smaller reduced area undergo
tank-treading motions. As mentioned earlier, tank treading occurs when
the top and bottom lubrication layers differ in size. The size of the
lubrication layers in all six cases are in Figure~\ref{fig:lubrication}.

@@

The tank-treading velocities of the examples with reduced area $\alpha =
0.4$ are in Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the
dashed black lines are also included, and the four marker points are the
Lagrangian points where the tangential velocities are computed. For
reduced area $\alpha = 0.4$, the single-component ($b=1$) and
multicomponent vesicles are clearly tank treading. Since the
single-component case has a larger difference between its top and bottom
boundary layers (see Figure~\ref{fig:lubrication)}, it tank treads
faster than the multicomponent case. In addition, since the top boundary
layer is larger in both cases, they both tank-tread in the same
direction---counterclockwise. In contrast, the single-component vesicle
with $b=0.55$ tank-treads in the clockwise direction; note, however,
that this example is still undergoing some deformations, so a constant
tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
undergoes deformations while in the stenosis, and a constant
tank-treading velocity is not observed

@@

While the size of the lubrication layers affect the tank-treading
behavior and the excess pressure, it has almost no effect on the
migration speed of the vesicle. 
%In Figure~\ref{fig:vesVelocity}, we plot
%the average velocity of the vesicle as it passes through the stenosed
%region.
With the exception of the single-component vesicle with $b=1$ and
$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
average vesicle speed is constant. Obviously, this average velocity
would be affected by the capillary number, $Ca$.

@@

Finally, we consider the three different energies---bending, tension,
and phase---for each of the single-component and multicomponent
vesicles. In Figure~\ref{fig:Energy}, we plot these energies as a
function of the vesicle's center of mass. As a reminder, the vesicle
enters the constriction at $x=-15$ and exits at $x=15$. Also note that
the single-component vesicle does not have a phase energy. A few general
trends can immediately be seen. First, as the vesicle enters the
stenosed region, there are sharp jumps in both the tension and bending
energies, as expected. Next, the multicomponent vesicles only coarsen
when the vesicle is not in the stenosed region. Finally, when coarsening
does occur, there are rapid changes in the tension energy.

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension
  (yellow), and phase (red) energies for a (a/b) single-component
  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
\end{figure}

@@

%\begin{itemize}

%    \item Comparison of different flow rates $\chi = 0.25 = 0.5 \mu m/s$ and $\chi = 2.5 = 5 \mu m/s$

%    \item Comparison of different reduced areas. Definitely interested in 0.40 and then maybe only one other value. A natural other value is 0.6 or 0.7 since this is close to the reduced area of a RBC.

%    \item Interesting tank treading/slipper shape when flow rate is 0.25 and reduced area is 0.4. We did not see this for any of the larger flow rates, and this is consistent with what is known about vesicles in a non-linear shear flow

%    \item Multicomponent goes through faster than single-component

%    \item Error in area is about 20X larger for the multicomponent
%    
%    \item How does the reduced area affect the speed of the vesicle and its ability to phase separate when i%n confinement. We haven't looked at a completed run with larger reduced area. Maybe there's one sitting on RCC or we% need to submit one?
%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in a narrowing geometry (Contracting)}
In this section, we consider a single vesicle passing through a geometry that slowly contracts to a region that is only 2~$\mu$m wide, and then immediately opens back up to a channel that is ten times larger. We first consider the effect of the initial lipid concentration when the floppy and stiff regions each make up half of the vesicle membrane. In Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha = 0.6$ with an initially random initial lipid concentration, one that is floppy in the front and stiff in the back, and one that is stiff in the front and floppy in the back. The vesicle with the random initial lipid distribution phase separates so that the floppy region is in the back and the stiff region is in the front. The vesicle where the initial lipid species distribution was fully phase separated and the floppy region was on the front of the vesicle began to reorient the floppy region to the back of the vesicle, making it partway after passing through the contraction. In the case where the initial lipid species distribution was fully phase separated and the floppy region was on the back of the vesicle, the floppy region remained on the the back of the vesicle. In all cases, the floppy regions were being oriented to cover the regions of the vesicle with the highest curvature to minimize the overall bending energy. Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions of high curvature are located in the back of the vesicle, we expect the overall bending energies to be lowest for the randomly distributed case and the fully separated floppy region on the back case. We observe this in Figure~\ref{fig:RAp6leftRightRandBending} Therefore, in all subsequent examples, we start with symmetric vesicle whose floppy region is in the back and its stiff region is in the front.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
    \caption{The bending energy of a multicomponent vesicle that is 50\% stiff with an initial phase separation to the left (blue), to the right (red), randomly distributed (yellow). The vesicle exits the contraction $x \approx 15$.}
    \label{fig:RAp6leftRightRandBending}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). We considered a semipermeable vesicle suspended in these
same geometries in our previous work~\cite{qua-gan-you2021}. All the
multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
For the single-component case, we consider two bending stiffnesses:
$b(u) = 1$ and $b(u) = 0.55$ which is the average bending stiffness of a
multicomponent vesicle whose stiff and floppy regions have the same
area. Throughout this section we plot the position of the vesicle in
terms of the $x$-coordinate of its center of mass. For the stenosed
geometry in Section~\ref{subsec:Stenosis}, the narrow region begins at
$x=-15$ and ends at $x=15$. For the contracting geometry in
Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
and reaches its narrowest point at $x=15$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Stenosis}A multicomponent vesicle in the
stenosis geometry}

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.
Figure~\ref{fig:RA6} shows six time steps of a single-component vesicle
with bending stiffness (a) $b=1$ and (b) $b=0.55$, and (c) a
multicomponent vesicle with an initially random distribution of lipids.
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new bending modulus~\eqref{eqn:tanhBending}. A single Lagrangian point
is included to visualize tank-treading behavior. There are slight
differences between the three cases, with the most noticeable being that
the multicomponent vesicle has higher curvature in the floppy region. We
consider the same setup in Figure~\ref{fig:RA4}, but the vesicle has
reduced area $\alpha = 0.4$. We first consider the three different
energies---bending, tension, and phase---for each of the
single-component and multicomponent vesicles. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center of mass. As a reminder, the vesicle enters the
constriction at $x=-15$ and exits at $x=15$. Also note that the
single-component vesicle does not have a phase energy. A few general
trends can immediately be seen. First, as the vesicle enters the
stenosis, there are sharp jumps in both the tension and bending
energies, as expected. Next, the multicomponent vesicles only coarsen
when the vesicle is not in the stenosis. Finally, when coarsening does
occur, there are rapid changes in the tension energy.

\begin{figure}
  \begin{minipage}{0.49\columnwidth}
    \centering
%    \subfigimg[width = \columnwidth, trim = {1cm 20cm 1cm 3cm}, clip]{(a)}{figures/RAp4BkgrdFlow.pdf}
    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\columnwidth}
    \centering
    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
  \end{minipage}
  \caption{\label{fig:Energy} \small The Bending (blue), tension
  (yellow), and phase (red) energies for a (a/b) single-component
  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
  \todo[inline]{need to redo these plots}
\end{figure}

A main difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers in all six cases are
in Figure~\ref{fig:lubrication}. The tank-treading velocities of the
examples with reduced area $\alpha = 0.4$ are in
Figure~\ref{fig:tankTreadRAp4}. The vesicle shapes at the dashed black
lines are also included, and the four marker points are the Lagrangian
points where the tangential velocities are computed. For reduced area
$\alpha = 0.4$, the single-component ($b=1$) and multicomponent vesicles
are clearly tank treading. Since the single-component case has a larger
difference between its top and bottom boundary layers (see
Figure~\ref{fig:lubrication}), it tank treads faster than the
multicomponent case. In addition, since the top boundary layer is larger
in both cases, they both tank-tread in the same
direction---counterclockwise. In contrast, the single-component vesicle
with $b=0.55$ tank-treads in the clockwise direction; note, however,
that this example is still undergoing some deformations, so a constant
tank-treading velocity is not observed. When $\alpha = 0.6$, the vesicle
undergoes deformations while in the stenosis, and a constant
tank-treading velocity is not observed

@@

@@

While the size of the lubrication layers affect the tank-treading
behavior and the excess pressure, it has almost no effect on the
migration speed of the vesicle. 
%In Figure~\ref{fig:vesVelocity}, we plot
%the average velocity of the vesicle as it passes through the stenosed
%region.
With the exception of the single-component vesicle with $b=1$ and
$\alpha = 0.6$, which has an average vesicle speed about 5\% slower, the
average vesicle speed is constant. Obviously, this average velocity
would be affected by the capillary number.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a single vesicle passing through a geometry
that slowly contracts to a region that is only 2~$\mu$m wide, and then
immediately opens back up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha =
0.6$ with an initially random initial lipid concentration, one that is
floppy in the front and stiff in the back, and one that is stiff in the
front and floppy in the back. The vesicle with the random initial lipid
distribution phase separates so that the floppy region is in the back
and the stiff region is in the front. The vesicle where the initial
lipid species distribution was fully phase separated and the floppy
region was on the front of the vesicle began to reorient the floppy
region to the back of the vesicle, making it partway after passing
through the contraction. In the case where the initial lipid species
distribution was fully phase separated and the floppy region was on the
back of the vesicle, the floppy region remained on the back of the
vesicle. In all cases, the floppy regions were being oriented to cover
the regions of the vesicle with the highest curvature to minimize the
overall bending energy. Since we can see in
Figure~\ref{fig:RA6leftRightRand} that the regions of high curvature are
located in the back of the vesicle, we expect the overall bending
energies to be lowest for the randomly distributed case and the fully
separated floppy region on the back case. We observe this in
Figure~\ref{fig:RAp6leftRightRandBending} Therefore, in all subsequent
examples, we start with symmetric vesicle whose floppy region is in the
back and its stiff region is in the front.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/bending_leftRightRand.pdf}
  \caption{\label{fig:RAp6leftRightRandBending} The bending energy of a
  multicomponent vesicle that is 50\% stiff with an initial phase
  separation to the left (blue), to the right (red), randomly
  distributed (yellow). The vesicle exits the contraction $x \approx
  15$.} 
\end{figure}
